---
title: "Sexual selection on floral traits"
format: 
  html:
    theme: cosmo
    toc: true
execute:
  echo: false
  warning: false
  message: false
  freeze: false
editor: visual
runtime: shiny
editor_options: 
  chunk_output_type: console
bibliography: references.bib
csl: styles/proceedings-of-the-royal-society-b.csl
---

```{r setup, include=FALSE}
# Remove messages containing "Attachement du package"
knitr::knit_hooks$set(message = function(x, options) {
  if (grepl("Attachement du package", x)) {
    return("")
  }
  return(x)
})

library(ggplot2)
library(tidyverse)
```

Visualize the pipeline analyses:

```{r,echo=FALSE,message=FALSE,warning=FALSE}
targets::tar_visnetwork()
```

WARNING !!!!!!!!!
oms (both at the flower or the id scale) is encoded as following: if it has not been
visited at all (i.e. oms including itself = 0), then oms = NA. Otherwise, oms is a true zero
because it can reproduce through selfing. BUT this is valuable only when reproductive success
include selfing (as in the first manuscript, to keep consistancy); if we focus on outcrossed
reproductive success, then null oms should not exist.

# Level of polyandry on flowers

```{r,echo=FALSE,message=FALSE,warning=FALSE}
targets::tar_load(oms_flower)

oms_flower$anova_flower
oms_flower$tukey_flower
oms_flower$plot_flower
```

# Level of polyandry on individuals

```{r,echo=FALSE,message=FALSE,warning=FALSE}
targets::tar_load(oms_id)

oms_id$anova_id
oms_id$tukey_id
oms_id$plot_id
```

# Path analysis with oms

We measured:

-   **nb_flo:** the number of "receptive" flowers

-   **nb_flo_open:** the number of opened flowers (including very new ones)

-   **nb_flo_all:** the total number of flowers (including very new and old ones)

-   **height_max:** the height of the highest flower

-   **height_mean:** the mean height of the highest flowers on each stem

-   **nb_stem:** the number of stems

Best way to do this analysis: SEM for the direct and indirect effect on oms and rs?

We proceed per sex and per treatment, as we saw that (i) there is an effect of ttt at least on oms and (ii) rs is different (contrary to oms) between sexual function, and there are biological hypotheses on a different effect of floral traits between sexual function.

## total rs

### With nb_flo_open and height_mean

**For the low treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_low_fem_combi1)
piecewise_low_fem_combi1$plot
```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_low_mal_combi1)
piecewise_low_mal_combi1$plot

```
:::
:::::

**For the medium treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_medium_fem_combi1)
piecewise_medium_fem_combi1$plot

```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_medium_mal_combi1)
piecewise_medium_mal_combi1$plot

```
:::
:::::

**For the high treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_high_fem_combi1)
piecewise_high_fem_combi1$plot

```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_high_mal_combi1)
piecewise_high_mal_combi1$plot
```
:::
:::::

> -   Always positive bateman gradients in both sexes
> -   For males only, flower number under natural selection in high treatment
> -   For the latter point, check with paternity share if it is mediated by more ovules fertilized

### With nb_flo_open and height_max

**For the low treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_low_fem_combi2)
piecewise_low_fem_combi2$plot
```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_low_mal_combi2)
piecewise_low_mal_combi2$plot

```
:::
:::::

**For the medium treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_medium_fem_combi2)
piecewise_medium_fem_combi2$plot

```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_medium_mal_combi2)
piecewise_medium_mal_combi2$plot

```
:::
:::::

**For the high treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_high_fem_combi2)
piecewise_high_fem_combi2$plot

```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_high_mal_combi2)
piecewise_high_mal_combi2$plot
```
:::
:::::

> -   Always positive bateman gradients in both sexes
> -   For males only, flower number under natural selection in high treatment
> -   For the latter point, check with paternity share if it is mediated by more ovules fertilized

### With nb_flo_all and height_mean

**For the low treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_low_fem_combi3)
piecewise_low_fem_combi3$plot
```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_low_mal_combi3)
piecewise_low_mal_combi3$plot

```
:::
:::::

**For the medium treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_medium_fem_combi3)
piecewise_medium_fem_combi3$plot

```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_medium_mal_combi3)
piecewise_medium_mal_combi3$plot

```
:::
:::::

**For the high treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_high_fem_combi3)
piecewise_high_fem_combi3$plot

```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_high_mal_combi3)
piecewise_high_mal_combi3$plot
```
:::
:::::

> -   Always positive bateman gradients in both sexes
> -   For males only, flower number under natural selection in high treatment
> -   For the latter point, check with paternity share if it is mediated by more ovules fertilized

### With nb_flo_all and height_max

**For the low treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_low_fem_combi4)
piecewise_low_fem_combi4$plot
```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_low_mal_combi4)
piecewise_low_mal_combi4$plot

```
:::
:::::

**For the medium treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_medium_fem_combi4)
piecewise_medium_fem_combi4$plot

```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_medium_mal_combi4)
piecewise_medium_mal_combi4$plot

```
:::
:::::

**For the high treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_high_fem_combi4)
piecewise_high_fem_combi4$plot

```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_high_mal_combi4)
piecewise_high_mal_combi4$plot
```
:::
:::::

> -   Always positive bateman gradients in both sexes
> -   For males only, flower number under natural selection in high treatment
> -   For the latter point, check with paternity share if it is mediated by more ovules fertilized

### With nb_stem and height_mean

**For the low treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_low_fem_combi5)
piecewise_low_fem_combi5$plot
```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_low_mal_combi5)
piecewise_low_mal_combi5$plot

```
:::
:::::

**For the medium treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_medium_fem_combi5)
piecewise_medium_fem_combi5$plot

```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_medium_mal_combi5)
piecewise_medium_mal_combi5$plot

```
:::
:::::

**For the high treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_high_fem_combi5)
piecewise_high_fem_combi5$plot

```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_high_mal_combi5)
piecewise_high_mal_combi5$plot
```
:::
:::::

> -   Always positive bateman gradients in both sexes
> -   For males only, flower number under natural selection in high treatment
> -   For the latter point, check with paternity share if it is mediated by more ovules fertilized

### With nb_stem and height_max

**For the low treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_low_fem_combi6)
piecewise_low_fem_combi6$plot
```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_low_mal_combi6)
piecewise_low_mal_combi6$plot

```
:::
:::::

**For the medium treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_medium_fem_combi6)
piecewise_medium_fem_combi6$plot

```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_medium_mal_combi6)
piecewise_medium_mal_combi6$plot

```
:::
:::::

**For the high treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_high_fem_combi6)
piecewise_high_fem_combi6$plot

```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_high_mal_combi6)
piecewise_high_mal_combi6$plot
```
:::
:::::

> -   Always positive bateman gradients in both sexes
> -   For males only, flower number under natural selection in high treatment
> -   For the latter point, check with paternity share if it is mediated by more ovules fertilized

## outcross rs

### With nb_flo_open and height_mean

**For the low treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_sr_low_fem_combi1)
piecewise_low_fem_combi1$plot
```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_sr_low_mal_combi1)
piecewise_low_mal_combi1$plot

```
:::
:::::

**For the medium treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_sr_medium_fem_combi1)
piecewise_medium_fem_combi1$plot

```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_sr_medium_mal_combi1)
piecewise_medium_mal_combi1$plot

```
:::
:::::

**For the high treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_sr_high_fem_combi1)
piecewise_high_fem_combi1$plot

```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_sr_high_mal_combi1)
piecewise_high_mal_combi1$plot
```
:::
:::::

> -   Always positive bateman gradients in both sexes
> -   For males only, flower number under natural selection in high treatment
> -   For the latter point, check with paternity share if it is mediated by more ovules fertilized

### With nb_flo_open and height_max

**For the low treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_sr_low_fem_combi2)
piecewise_low_fem_combi2$plot
```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_sr_low_mal_combi2)
piecewise_low_mal_combi2$plot

```
:::
:::::

**For the medium treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_sr_medium_fem_combi2)
piecewise_medium_fem_combi2$plot

```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_sr_medium_mal_combi2)
piecewise_medium_mal_combi2$plot

```
:::
:::::

**For the high treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_sr_high_fem_combi2)
piecewise_high_fem_combi2$plot

```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_sr_high_mal_combi2)
piecewise_high_mal_combi2$plot
```
:::
:::::

> -   Always positive bateman gradients in both sexes
> -   For males only, flower number under natural selection in high treatment
> -   For the latter point, check with paternity share if it is mediated by more ovules fertilized

### With nb_flo_all and height_mean

**For the low treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_sr_low_fem_combi3)
piecewise_low_fem_combi3$plot
```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_sr_low_mal_combi3)
piecewise_low_mal_combi3$plot

```
:::
:::::

**For the medium treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_sr_medium_fem_combi3)
piecewise_medium_fem_combi3$plot

```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_sr_medium_mal_combi3)
piecewise_medium_mal_combi3$plot

```
:::
:::::

**For the high treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_sr_high_fem_combi3)
piecewise_high_fem_combi3$plot

```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_sr_high_mal_combi3)
piecewise_high_mal_combi3$plot
```
:::
:::::

> -   Always positive bateman gradients in both sexes
> -   For males only, flower number under natural selection in high treatment
> -   For the latter point, check with paternity share if it is mediated by more ovules fertilized

### With nb_flo_all and height_max

**For the low treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_sr_low_fem_combi4)
piecewise_low_fem_combi4$plot
```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_sr_low_mal_combi4)
piecewise_low_mal_combi4$plot

```
:::
:::::

**For the medium treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_sr_medium_fem_combi4)
piecewise_medium_fem_combi4$plot

```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_sr_medium_mal_combi4)
piecewise_medium_mal_combi4$plot

```
:::
:::::

**For the high treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_sr_high_fem_combi4)
piecewise_high_fem_combi4$plot

```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_sr_high_mal_combi4)
piecewise_high_mal_combi4$plot
```
:::
:::::

> -   Always positive bateman gradients in both sexes
> -   For males only, flower number under natural selection in high treatment
> -   For the latter point, check with paternity share if it is mediated by more ovules fertilized

### With nb_stem and height_mean

**For the low treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_sr_low_fem_combi5)
piecewise_low_fem_combi5$plot
```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_sr_low_mal_combi5)
piecewise_low_mal_combi5$plot

```
:::
:::::

**For the medium treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_sr_medium_fem_combi5)
piecewise_medium_fem_combi5$plot

```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_sr_medium_mal_combi5)
piecewise_medium_mal_combi5$plot

```
:::
:::::

**For the high treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_sr_high_fem_combi5)
piecewise_high_fem_combi5$plot

```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_sr_high_mal_combi5)
piecewise_high_mal_combi5$plot
```
:::
:::::

> -   Always positive bateman gradients in both sexes
> -   For males only, flower number under natural selection in high treatment
> -   For the latter point, check with paternity share if it is mediated by more ovules fertilized

### With nb_stem and height_max

**For the low treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_sr_low_fem_combi6)
piecewise_low_fem_combi6$plot
```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_sr_low_mal_combi6)
piecewise_low_mal_combi6$plot

```
:::
:::::

**For the medium treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_sr_medium_fem_combi6)
piecewise_medium_fem_combi6$plot

```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_sr_medium_mal_combi6)
piecewise_medium_mal_combi6$plot

```
:::
:::::

**For the high treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_sr_high_fem_combi6)
piecewise_high_fem_combi6$plot

```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_sr_high_mal_combi6)
piecewise_high_mal_combi6$plot
```
:::
:::::

> -   Always positive bateman gradients in both sexes
> -   For males only, flower number under natural selection in high treatment
> -   For the latter point, check with paternity share if it is mediated by more ovules fertilized

# Path analysis with oms and post-poll process

For males, we estimate the paternity share by excluding selfing in order to be consistant with oms. Paternity share is the proportion of genotyped seeds sired by a focal father. We can also do the analysis by integrating selfing events in the estimation of paternity share (mean_ps_all).

For females, post-poll process are more difficult to define: the diversity of sexual partners that had reached ovules matter (?) but here we define post-poll as the partner ability to fertilize ovules ("from the female point of view, to which point she has gathered a good team which score a lot of points") but note that we did not categorize this as as post-poll process in the abundance paper )

### With nb_flo_open and height_mean (sr all)

**For the low treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisefemales_low_combi1)
piecewisefemales_low_combi1$plot
```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisemales_low_combi1)
piecewisemales_low_combi1$plot

```
:::
:::::

**For the medium treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisefemales_medium_combi1)
piecewisefemales_medium_combi1$plot
```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisemales_medium_combi1)
piecewisemales_medium_combi1$plot

```
:::
:::::

**For the high treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisefemales_high_combi1)
piecewisefemales_high_combi1$plot
```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisemales_high_combi1)
piecewisemales_high_combi1$plot

```
:::
:::::

### With nb_flo_all and height_mean (sr all)

**For the low treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisefemales_low_combi3)
piecewisefemales_low_combi3$plot
```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisemales_low_combi3)
piecewisemales_low_combi3$plot

```
:::
:::::

**For the medium treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisefemales_medium_combi3)
piecewisefemales_medium_combi3$plot
```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisemales_medium_combi3)
piecewisemales_medium_combi3$plot

```
:::
:::::

**For the high treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisefemales_high_combi3)
piecewisefemales_high_combi3$plot
```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisemales_high_combi3)
piecewisemales_high_combi3$plot

```
:::
:::::

### With nb_flo_open and height_mean (sr outcrossed)

**For the low treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisefemales_sr_low_combi1)
piecewisefemales_sr_low_combi1$plot
```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisemales_sr_low_combi1)
piecewisemales_sr_low_combi1$plot

```
:::
:::::

**For the medium treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisefemales_sr_medium_combi1)
piecewisefemales_sr_medium_combi1$plot
```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisemales_sr_medium_combi1)
piecewisemales_sr_medium_combi1$plot

```
:::
:::::

**For the high treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisefemales_sr_high_combi1)
piecewisefemales_sr_high_combi1$plot
```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisemales_sr_high_combi1)
piecewisemales_sr_high_combi1$plot

```
:::
:::::

## Test with brms: pool everything

With total rs and nb_flo_all and height_mean

**All sex and ttt :**

```{r,echo=FALSE,warning=FALSE,message=FALSE}

targets::tar_load(brms_pooled_data)

brms_pooled_data$summary

```

> The only thing that we can conclude is that flower number increase reproductive success in the high treatment for the female function, and that this effect is less strong for the male function
