---
title: "Sexual selection on floral traits"
format: 
  html:
    theme: cosmo
    toc: true
execute:
  echo: false
  warning: false
  message: false
  freeze: false
editor: visual
runtime: shiny
editor_options: 
  chunk_output_type: console
bibliography: references.bib
csl: styles/proceedings-of-the-royal-society-b.csl
---

```{r setup, include=FALSE}
# Remove messages containing "Attachement du package"
knitr::knit_hooks$set(message = function(x, options) {
  if (grepl("Attachement du package", x)) {
    return("")
  }
  return(x)
})

library(ggplot2)
library(tidyverse)
```

Visualize the pipeline analyses:

```{r,echo=FALSE,message=FALSE,warning=FALSE}
targets::tar_visnetwork()
```

WARNING !!!!!!!!! oms (both at the flower or the id scale) is encoded as following: if it has not been visited at all (i.e. oms including itself = 0), then oms = NA. Otherwise, oms is a true zero because it can reproduce through selfing. BUT this is valuable only when reproductive success include selfing (as in the first manuscript, to keep consistancy); if we focus on outcrossed reproductive success, then null oms should not exist.

# Treatment effect on variables at the flower level

## oms

```{r,echo=FALSE,message=FALSE,warning=FALSE}
targets::tar_load(oms_flower)

oms_flower$anova_flower
oms_flower$tukey_flower
oms_flower$plot_flower
```

## nb_visit

```{r,echo=FALSE,message=FALSE,warning=FALSE}
targets::tar_load(visit_flower)

visit_flower$anova_flower
visit_flower$tukey_flower
visit_flower$plot_flower
```

## pl 

```{r,echo=FALSE,message=FALSE,warning=FALSE}
targets::tar_load(pl_flower)

pl_flower$anova_flower
pl_flower$tukey_flower
pl_flower$plot_flower
```

## seeds

```{r,echo=FALSE,message=FALSE,warning=FALSE}
targets::tar_load(seeds_flower)

seeds_flower$anova_flower
seeds_flower$tukey_flower
seeds_flower$plot_flower
```

# Treatment effect on variables at the id level

## oms
```{r,echo=FALSE,message=FALSE,warning=FALSE}
targets::tar_load(oms_id)

oms_id$anova_id
oms_id$tukey_id
oms_id$plot_id
```

## sr
```{r,echo=FALSE,message=FALSE,warning=FALSE}
targets::tar_load(sr_id)

sr_id$anova_id
sr_id$tukey_id
sr_id$plot_id
```

## sr_all
```{r,echo=FALSE,message=FALSE,warning=FALSE}
targets::tar_load(sr_all_id)

sr_all_id$anova_id
sr_all_id$tukey_id
sr_all_id$plot_id
```

## mean_ps
```{r,echo=FALSE,message=FALSE,warning=FALSE}
targets::tar_load(mean_ps_id)

mean_ps_id$anova_id
mean_ps_id$tukey_id
mean_ps_id$plot_id
```

## diff_q
```{r,echo=FALSE,message=FALSE,warning=FALSE}
targets::tar_load(diff_q_id)

diff_q_id$anova_id
diff_q_id$tukey_id
diff_q_id$plot_id
```

## contact_id
```{r,echo=FALSE,message=FALSE,warning=FALSE}
targets::tar_load(contid_id)

contid_id$anova_id
contid_id$tukey_id
contid_id$plot_id
```

## mean_position
```{r,echo=FALSE,message=FALSE,warning=FALSE}
targets::tar_load(meanpos_id)

meanpos_id$anova_id
meanpos_id$tukey_id
meanpos_id$plot_id
```

## nb flower visited
```{r,echo=FALSE,message=FALSE,warning=FALSE}
targets::tar_load(flo_id)

flo_id$anova_id
flo_id$tukey_id
flo_id$plot_id
```

## nb visit per flower
```{r,echo=FALSE,message=FALSE,warning=FALSE}
targets::tar_load(visflo_id)

visflo_id$anova_id
visflo_id$tukey_id
visflo_id$plot_id
```

## dur visit
```{r,echo=FALSE,message=FALSE,warning=FALSE}
targets::tar_load(durvis_id)

durvis_id$anova_id
durvis_id$tukey_id
durvis_id$plot_id
```
# MANOVA

```{r,echo=FALSE,message=FALSE,warning=FALSE}
targets::tar_load(data_id)

data_id |>
  group_by(ttt) |>
  summarise(mean_flower = mean(nb_flo_open, na.rm = T),
            sd_dlower = sd(nb_flo_open, na.rm = T))
```

# Path analysis with oms and post-poll process

We measured:

-   **nb_flo:** the number of "receptive" flowers

-   **nb_flo_open:** the number of opened flowers (including very new ones)

-   **nb_flo_all:** the total number of flowers (including very new and old ones)

-   **height_max:** the height of the highest flower

-   **height_mean:** the mean height of the highest flowers on each stem

-   **nb_stem:** the number of stems

Best way to do this analysis: SEM for the direct and indirect effect on oms and rs?

We proceed per sex and per treatment, as we saw that (i) there is an effect of ttt at least on oms and (ii) rs is different (contrary to oms) between sexual function, and there are biological hypotheses on a different effect of floral traits between sexual function.

For males, we estimate the paternity share by excluding selfing in order to be consistant with oms. Paternity share is the proportion of genotyped seeds sired by a focal father. We can also do the analysis by integrating selfing events in the estimation of paternity share (mean_ps_all).

For females, post-poll process are more difficult to define: the diversity of sexual partners that had reached ovules matter (?) but here we define post-poll as the partner ability to fertilize ovules ("from the female point of view, to which point she has gathered a good team which score a lot of points") but note that we did not categorize this as as post-poll process in the abundance paper )

### With nb_flo_open and height_mean (sr all)

**For the low treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisefemales_low_combi1)
piecewisefemales_low_combi1$plot
piecewisefemales_low_combi1$summary
```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisemales_low_combi1)
piecewisemales_low_combi1$plot
piecewisemales_low_combi1$summary

```
:::
:::::

**For the medium treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisefemales_medium_combi1)
piecewisefemales_medium_combi1$plot
piecewisefemales_medium_combi1$summary
```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisemales_medium_combi1)
piecewisemales_medium_combi1$plot
piecewisemales_medium_combi1$summary

```
:::
:::::

**For the high treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisefemales_high_combi1)
piecewisefemales_high_combi1$plot
piecewisefemales_high_combi1$summary
```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisemales_high_combi1)
piecewisemales_high_combi1$plot
piecewisemales_high_combi1$summary

```
:::
:::::

### With nb_flo_all and height_mean (sr all)

**For the low treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisefemales_low_combi3)
piecewisefemales_low_combi3$plot
```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisemales_low_combi3)
piecewisemales_low_combi3$plot

```
:::
:::::

**For the medium treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisefemales_medium_combi3)
piecewisefemales_medium_combi3$plot
```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisemales_medium_combi3)
piecewisemales_medium_combi3$plot

```
:::
:::::

**For the high treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisefemales_high_combi3)
piecewisefemales_high_combi3$plot
```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisemales_high_combi3)
piecewisemales_high_combi3$plot

```
:::
:::::

### With nb_flo and height_mean (sr all)

**For the low treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisefemales_low_combi7)
piecewisefemales_low_combi7$plot
```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisemales_low_combi7)
piecewisemales_low_combi7$plot

```
:::
:::::

**For the medium treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisefemales_medium_combi7)
piecewisefemales_medium_combi7$plot
```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisemales_medium_combi7)
piecewisemales_medium_combi7$plot
piecewisemales_medium_combi7$summary
```
:::
:::::

**For the high treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisefemales_high_combi7)
piecewisefemales_high_combi7$plot
```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisemales_high_combi7)
piecewisemales_high_combi7$plot

```
:::
:::::

### With nb_flo_open and height_mean (sr outcrossed)

**For the low treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisefemales_sr_low_combi1)
piecewisefemales_sr_low_combi1$plot
piecewisefemales_sr_low_combi1$summary
```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisemales_sr_low_combi1)
piecewisemales_sr_low_combi1$plot

```
:::
:::::

**For the medium treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisefemales_sr_medium_combi1)
piecewisefemales_sr_medium_combi1$plot
```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisemales_sr_medium_combi1)
piecewisemales_sr_medium_combi1$plot

```
:::
:::::

**For the high treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisefemales_sr_high_combi1)
piecewisefemales_sr_high_combi1$plot
```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewisemales_sr_high_combi1)
piecewisemales_sr_high_combi1$plot

```
:::
:::::

<!-- ## Test with brms: pool everything -->

<!-- With total rs and nb_flo_all and height_mean -->

<!-- **All sex and ttt :** -->

<!-- ```{r,echo=FALSE,warning=FALSE,message=FALSE} -->

<!-- targets::tar_load(brms_pooled_data) -->

<!-- brms_pooled_data$summary -->

<!-- ``` -->

<!-- > The only thing that we can conclude is that flower number increase reproductive success in the high treatment for the female function, and that this effect is less strong for the male function -->

# SEM with pollinator visit proxies

With nb_flo_open and height_mean 

**For the low treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_visits_female_low)
piecewise_visits_female_low$plot
piecewise_visits_female_low$summary
```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_visits_male_low)
piecewise_visits_male_low$plot
piecewise_visits_male_low$summary
```
:::
:::::

**For the medium treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_visits_female_medium)
piecewise_visits_female_medium$plot
piecewise_visits_female_medium$summary
```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_visits_male_medium)
piecewise_visits_male_medium$plot
piecewise_visits_male_medium$summary

```
:::
:::::

**For the high treatment :**

::::: grid
::: g-col-6
Females:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_visits_female_high)
piecewise_visits_female_high$plot
piecewise_visits_female_high$summary
```
:::

::: g-col-6
Males:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(piecewise_visits_male_high)
piecewise_visits_male_high$plot
piecewise_visits_male_high$summary
```
:::
:::::

# SEM at the flower scale

**For the low treatment :**

```{r,echo=FALSE,warning=FALSE,message=FALSE}

targets::tar_load(piecewise_flower_low)
piecewise_flower_low$plot
piecewise_flower_low$summary

```

**For the medium treatment :**

```{r,echo=FALSE,warning=FALSE,message=FALSE}

targets::tar_load(piecewise_flower_medium)
piecewise_flower_medium$plot
piecewise_flower_medium$summary

```

**For the high treatment :**

```{r,echo=FALSE,warning=FALSE,message=FALSE}

targets::tar_load(piecewise_flower_high)
piecewise_flower_high$plot
piecewise_flower_high$summary

```