---
title: "Sexual selection on floral traits"
format: 
  html:
    theme: cosmo
    toc: true
execute:
  echo: false
  warning: false
  message: false
  freeze: false
editor: visual
runtime: shiny
editor_options: 
  chunk_output_type: console
bibliography: references.bib
csl: styles/proceedings-of-the-royal-society-b.csl
---

```{r setup, include=FALSE}
# Remove messages containing "Attachement du package"
knitr::knit_hooks$set(message = function(x, options) {
  if (grepl("Attachement du package", x)) {
    return("")
  }
  return(x)
})

library(ggplot2)
library(tidyverse)
```

Visualize the pipeline analyses:

```{r,echo=FALSE,message=FALSE,warning=FALSE}
targets::tar_visnetwork()
```

WARNING !!!!!!!!! oms (both at the flower or the id scale) is encoded as following: if it has not been visited at all (i.e. oms including itself = 0), then oms = NA. Otherwise, oms is a true zero because it can reproduce through selfing. BUT this is valuable only when reproductive success include selfing (as in the first manuscript, to keep consistancy); if we focus on outcrossed reproductive success, then null oms should not exist.

# Treatment effect on variables at the id level

## sr_all mal
```{r,echo=FALSE,message=FALSE,warning=FALSE}
targets::tar_load(sr_all_mal)

sr_all_mal$summary
sr_all_mal$lrt
sr_all_mal$tukey
```

## sr_all fem
```{r,echo=FALSE,message=FALSE,warning=FALSE}
targets::tar_load(sr_all_fem)

sr_all_fem$summary
sr_all_fem$lrt
sr_all_fem$tukey
sr_all_fem$plot
```

## sr_out mal
```{r,echo=FALSE,message=FALSE,warning=FALSE}
targets::tar_load(sr_out_mal)

sr_out_mal$summary
sr_out_mal$lrt
sr_out_mal$tukey
```

## sr_out fem
```{r,echo=FALSE,message=FALSE,warning=FALSE}
targets::tar_load(sr_out_fem)

sr_out_fem$summary
sr_out_fem$lrt
sr_out_fem$tukey
sr_out_fem$plot
```

## oms mal
```{r,echo=FALSE,message=FALSE,warning=FALSE}
targets::tar_load(oms_mal)

oms_mal$summary
oms_mal$lrt
oms_mal$tukey
```

## oms fem
```{r,echo=FALSE,message=FALSE,warning=FALSE}
targets::tar_load(oms_fem)

oms_fem$summary
oms_fem$lrt
oms_fem$tukey
oms_fem$plot
```

## mean_ps mal
```{r,echo=FALSE,message=FALSE,warning=FALSE}
targets::tar_load(mean_ps_mal)

mean_ps_mal$summary
mean_ps_mal$lrt
mean_ps_mal$tukey
mean_ps_mal$plot
```

## diff_q fem
```{r,echo=FALSE,message=FALSE,warning=FALSE}
targets::tar_load(diff_q_fem)

diff_q_fem$summary
diff_q_fem$lrt
diff_q_fem$tukey
diff_q_fem$plot
```

## contid (pla)
```{r,echo=FALSE,message=FALSE,warning=FALSE}
targets::tar_load(contid_id)

contid_id$summary
contid_id$lrt
contid_id$tukey
contid_id$plot
```

## meanpos
```{r,echo=FALSE,message=FALSE,warning=FALSE}
targets::tar_load(meanpos_id)

meanpos_id$summary
meanpos_id$lrt
meanpos_id$tukey
meanpos_id$plot
```

## visflo
```{r,echo=FALSE,message=FALSE,warning=FALSE}
targets::tar_load(visflo_id)

visflo_id$summary
visflo_id$lrt
visflo_id$tukey
visflo_id$plot
```

## flo
```{r,echo=FALSE,message=FALSE,warning=FALSE}
targets::tar_load(flo_id)

flo_id$summary
flo_id$lrt
flo_id$tukey
flo_id$plot
```
# MANOVA

```{r,echo=FALSE,message=FALSE,warning=FALSE}
targets::tar_load(data_id)

data_id |>
  group_by(ttt) |>
  summarise(mean_flower = mean(nb_flo_open, na.rm = T),
            sd_dlower = sd(nb_flo_open, na.rm = T))
```

# Basic SEMs

## Males

**For the low treatment :**

```{r,echo=FALSE,warning=FALSE,message=FALSE}

targets::tar_load(piecewise_males_low_combi1_wtot_basic)
piecewise_males_low_combi1_wtot_basic$plot
piecewise_males_low_combi1_wtot_basic$summary
piecewise_males_low_combi1_wtot_basic$dsep
```

**For the medium treatment :**

```{r,echo=FALSE,warning=FALSE,message=FALSE}

targets::tar_load(piecewise_males_medium_combi1_wtot_basic)
piecewise_males_medium_combi1_wtot_basic$plot
piecewise_males_medium_combi1_wtot_basic$summary
piecewise_males_medium_combi1_wtot_basic$dsep
```

**For the high treatment :**

```{r,echo=FALSE,warning=FALSE,message=FALSE}

targets::tar_load(piecewise_males_high_combi1_wtot_basic)
piecewise_males_high_combi1_wtot_basic$plot
piecewise_males_high_combi1_wtot_basic$summary
piecewise_males_high_combi1_wtot_basic$dsep
```

## Females

**For the low treatment :**

```{r,echo=FALSE,warning=FALSE,message=FALSE}

targets::tar_load(piecewise_females_low_combi1_wtot_basic)
piecewise_females_low_combi1_wtot_basic$plot
piecewise_females_low_combi1_wtot_basic$summary
piecewise_females_low_combi1_wtot_basic$dsep
```

**For the medium treatment :**

```{r,echo=FALSE,warning=FALSE,message=FALSE}

targets::tar_load(piecewise_females_medium_combi1_wtot_basic)
piecewise_females_medium_combi1_wtot_basic$plot
piecewise_females_medium_combi1_wtot_basic$summary
piecewise_females_medium_combi1_wtot_basic$dsep
```

**For the high treatment :**

```{r,echo=FALSE,warning=FALSE,message=FALSE}

targets::tar_load(piecewise_females_high_combi1_wtot_basic)
piecewise_females_high_combi1_wtot_basic$plot
piecewise_females_high_combi1_wtot_basic$summary
piecewise_females_high_combi1_wtot_basic$dsep
```

# Final SEMs

## Males

**For the low treatment :**

```{r,echo=FALSE,warning=FALSE,message=FALSE}

targets::tar_load(piecewise_males_low_combi1_wtot_final)
piecewise_males_low_combi1_wtot_final$plot
piecewise_males_low_combi1_wtot_final$summary
piecewise_males_low_combi1_wtot_final$dsep
knitr::kable(piecewise_males_low_combi1_wtot_final$coefs)
```

**For the medium treatment :**

```{r,echo=FALSE,warning=FALSE,message=FALSE}

targets::tar_load(piecewise_males_medium_combi1_wtot_final)
piecewise_males_medium_combi1_wtot_final$plot
piecewise_males_medium_combi1_wtot_final$summary
piecewise_males_medium_combi1_wtot_final$dsep
knitr::kable(piecewise_males_medium_combi1_wtot_final$coefs)
```

**For the high treatment :**

```{r,echo=FALSE,warning=FALSE,message=FALSE}

targets::tar_load(piecewise_males_high_combi1_wtot_final)
piecewise_males_high_combi1_wtot_final$plot
piecewise_males_high_combi1_wtot_final$summary
piecewise_males_high_combi1_wtot_final$dsep
knitr::kable(piecewise_males_high_combi1_wtot_final$coefs)
```

## Females

**For the low treatment :**

```{r,echo=FALSE,warning=FALSE,message=FALSE}

targets::tar_load(piecewise_females_low_combi1_wtot_final)
piecewise_females_low_combi1_wtot_final$plot
piecewise_females_low_combi1_wtot_final$summary
piecewise_females_low_combi1_wtot_final$dsep
knitr::kable(piecewise_females_low_combi1_wtot_final$coefs)
```

**For the medium treatment :**

```{r,echo=FALSE,warning=FALSE,message=FALSE}

targets::tar_load(piecewise_females_medium_combi1_wtot_final)
piecewise_females_medium_combi1_wtot_final$plot
piecewise_females_medium_combi1_wtot_final$summary
piecewise_females_medium_combi1_wtot_final$dsep
knitr::kable(piecewise_females_medium_combi1_wtot_final$coefs)
```

**For the high treatment :**

```{r,echo=FALSE,warning=FALSE,message=FALSE}

targets::tar_load(piecewise_females_high_combi1_wtot_final)
piecewise_females_high_combi1_wtot_final$plot
piecewise_females_high_combi1_wtot_final$summary
piecewise_females_high_combi1_wtot_final$dsep
knitr::kable(piecewise_females_high_combi1_wtot_final$coefs)
```

# Z-tests for comparison between SEM

```{r,echo=FALSE,warning=FALSE,message=FALSE}
targets::tar_load(z_tests)
knitr::kable(z_tests$intra_sex)
knitr::kable(z_tests$inter_sex)
```

# Final SEMs with outcrossed

## Males

**For the low treatment :**

```{r,echo=FALSE,warning=FALSE,message=FALSE}

targets::tar_load(piecewise_males_low_combi1_wout_final)
piecewise_males_low_combi1_wout_final$plot
piecewise_males_low_combi1_wout_final$summary
piecewise_males_low_combi1_wout_final$dsep
knitr::kable(piecewise_males_low_combi1_wout_final$coefs)
```

**For the medium treatment :**

```{r,echo=FALSE,warning=FALSE,message=FALSE}

targets::tar_load(piecewise_males_medium_combi1_wout_final)
piecewise_males_medium_combi1_wout_final$plot
piecewise_males_medium_combi1_wout_final$summary
piecewise_males_medium_combi1_wout_final$dsep
knitr::kable(piecewise_males_medium_combi1_wout_final$coefs)
```

**For the high treatment :**

```{r,echo=FALSE,warning=FALSE,message=FALSE}

targets::tar_load(piecewise_males_high_combi1_wout_final)
piecewise_males_high_combi1_wout_final$plot
piecewise_males_high_combi1_wout_final$summary
piecewise_males_high_combi1_wout_final$dsep
knitr::kable(piecewise_males_high_combi1_wout_final$coefs)
```

## Females

**For the low treatment :**

```{r,echo=FALSE,warning=FALSE,message=FALSE}

targets::tar_load(piecewise_females_low_combi1_wout_final)
piecewise_females_low_combi1_wout_final$plot
piecewise_females_low_combi1_wout_final$summary
piecewise_females_low_combi1_wout_final$dsep
knitr::kable(piecewise_females_low_combi1_wout_final$coefs)
```

**For the medium treatment :**

```{r,echo=FALSE,warning=FALSE,message=FALSE}

targets::tar_load(piecewise_females_medium_combi1_wout_final)
piecewise_females_medium_combi1_wout_final$plot
piecewise_females_medium_combi1_wout_final$summary
piecewise_females_medium_combi1_wout_final$dsep
knitr::kable(piecewise_females_medium_combi1_wout_final$coefs)
```

**For the high treatment :**

```{r,echo=FALSE,warning=FALSE,message=FALSE}

targets::tar_load(piecewise_females_high_combi1_wout_final)
piecewise_females_high_combi1_wout_final$plot
piecewise_females_high_combi1_wout_final$summary
piecewise_females_high_combi1_wout_final$dsep
knitr::kable(piecewise_females_high_combi1_wout_final$coefs)
```
